---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE, eval = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# sfExtras

<!-- badges: start -->
<!-- badges: end -->

The goal of sfExtras is to provide a nice interface to sf-style functions for spatial 
autocorrelation functionality in R. This package was developed for the R Spatial Workshop
at the [Center for Spatial Data Science](https://spatial.uchicago.edu/) at the University
of Chicago. The code in this package originates from documentation
from [sf](https://github.com/r-spatial/sf) and [spdep](https://github.com/r-spatial/spdep).
The goal is to create a nice function API interface for spatial analysts 
to use with the sf and spdep packages.

**Disclaimer**: This package is still heavily under development, so use at your own risk.
PRs and issues are welcome.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("spatialanalysis/sfExtras")
```
## Example

Load the sfExtras library, then start making contiguity weights:

```{r weights}
library(sf)
library(sfExtras)
library(geodaData)

ncovr_rook <- st_rook(ncovr)
ncovr_queen <- st_queen(ncovr)
```

Convert into **nb** class for use with the spdep package:

```{r as_nb}
rook_nb <- st_as_nb(ncovr_rook)
```
